
\documentclass[letterpaper,10pt]{article}
\usepackage{amsmath,color}

\definecolor{darkblue}{rgb}{0,0,0.35}
\definecolor{lightgray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.4,0.4,0.7}

\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}

%% set spacings
%%\linespread{1.0} %% comment out this line if not using charter font
\usepackage[hmargin=2cm,vmargin=1.5cm]{geometry}
\newcommand{\vsp}{\vspace{2pc}}
\setlength\parindent{0pt} %% Sets indent space to 0
\renewcommand{\indent}{\hspace{3pc}}

\newcommand{\mblue}{\color{darkblue}}

\begin{document}

\pagestyle{empty}

{\mblue\rule{4.63in}{0.08cm}}

\vspace{-1.0pc}
\hfill{\Huge\mblue Riann Sahnow}
\smallbreak{\hfill{\footnotesize riann.sahnow@gmail.com\qquad 651-245-5823}}

\vspace{2pc}
To Whom It May Concern:

\bigbreak\qquad I am writing this letter in regards to the open elementary teaching
positions in the 27J School District. I learned about these positions through
the 27J website and they interest me greatly. I have worked in early childhood
education and family services counseling since 2000 and completed
my Colorado Initial Teacher License in May of 2019 through the Friends School Teacher Preparation
Program. I am currently searching for an elementary teacher position as I finish
an M.A. at the University of Colorado--Denver.

\bigbreak\qquad Through my passion for teaching and my experience in
human development, I thrive in creating, growing, and sustaining a space in
my classroom that cares for and positively affects the learning of each student
individually. I strive to offer students choices in their learning to help them
develop strengths and interests. Assessments are used to inform instruction and
scaffold students in a way that meets them where they are and assists them in
achieving their potential.

\bigbreak\qquad One of my greatest passions in education is creating
a community focused on strong relationships between students, teachers, and
families. My goal for the classroom community is to create an environment
where every child feels seen and heard, and where each student is comfortable
taking risks by experimenting, sharing ideas, giving feedback to others, learning,
and growing both socially and emotionally.


\bigbreak\qquad I believe that my background and teaching philosophy, combined
with my ability to facilitate constructive learning environments with engaging
lessons for small and large groups of children, make me an ideal candidate for
this role.

\bigbreak\qquad Attached is my resume for further reference. I would enjoy
discussing these positions and am happy to provide any additional
information if needed. Thank you for your time and consideration.

\bigbreak Sincerely,

\vspace{2pc} Riann Sahnow


\end{document}


























