
\documentclass[letterpaper,10pt]{article}
\usepackage{amsmath,color}

\definecolor{darkblue}{rgb}{0,0,0.35}
\definecolor{lightgray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.4,0.4,0.7}

\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}

%% set spacings
%%\linespread{1.0} %% comment out this line if not using charter font
\usepackage[hmargin=2cm,vmargin=1.5cm]{geometry}
\newcommand{\vsp}{\vspace{2pc}}
\setlength\parindent{0pt} %% Sets indent space to 0
\renewcommand{\indent}{\hspace{3pc}}

\newcommand{\mblue}{\color{darkblue}}

\begin{document}

\pagestyle{empty}

{\mblue\rule{4.63in}{0.08cm}}

\vspace{-1.0pc}
\hfill{\Huge\mblue Riann Sahnow}
\smallbreak{\hfill{\footnotesize riann.sahnow@gmail.com\qquad 651-245-5823}}

\vspace{2pc}
\qquad\qquad I am an experienced teacher of 15 years, currently completing a program pursuing a Colorado elementary teaching license with the Friends Teacher Preparation Program. I am dedicated to
building inclusive and equitable relationships with students, parents, and colleagues to create an engaging and collaborative learning environment that contributes to each child's
success.
\section*{\mblue Professional Experience}

\vspace{-2.15pc}
{\hfill\mblue\rule{4.615in}{0.02cm}}

\vspace{1pc}
\textbf{Boulder Country Day School}\hfill Teacher Candidate -- Friends School Teacher Preparation Program
\smallbreak Gunbarrel, CO\hfill Aug 2018 -- May 2019

\begin{itemize}
    \item One year of classroom experience in elementary education.
    \item Planned and implemented a thematic unit about the Boulder County Watershed.
    \item Use reflective analysis of instructional strategies to create intentional and engaging lessons, creating interactive learning opportunities for each child.
    \item Collaborate with colleagues on student projects.
\end{itemize}


\vspace{1pc}
\textbf{Treehouse Learning, LLC}\hfill Lead Teacher \& Preschool Lead
\smallbreak Louisville, CO\hfill Aug 2009 -- July 2018

\begin{itemize}
    \item Experienced teacher with an average of 27 students.
    \item Research, design, and implement innovative and engaging lesson plans and activities that develop intellectual, physical, and social/emotional learning.
    \item Successfully improve student participation in the classroom through integration of creative role-playing exercises.
    \item Successfully reduced student behavior issues by establishing a strong teamwork environment.
    \item Explore and implement project-based learning that allows students to become better self-learners.
    \item Plan, implement, monitor, and assess student development through individual observations and documentation.
    \item In two months, increased literacy skills of Pre-K students to 90\% of children recognizing
    all letters of the alphabet and 50\% of children knowing all letter sounds.
    \item Created individualized goal sheets to differentiate and scaffold children's learning and document progress.
    \item Develop reciprocal, culturally responsive relationships with families and community to improve communication
    and trust between teachers, students, and parents.
    \item Track and meet yearly continuing education guidelines to implement new knowledge in the classroom setting.
    \item Analyzed Colorado Academic Standards (CAS) in order to create and develop child assessment forms.
    \item Act as a liaison between teaching teams and administration to maintain policies, solve problems, and improve curriculum.
    \item Train and mentor diverse teaching teams with successful outcomes in classroom management, behavior management, and curriculum focused strategies.
\end{itemize}

\pagebreak
\textbf{Peace of Mind Early Education}\hfill Lead Teacher \& Program Coordinator
\smallbreak Woodbury, MN\hfill Sep 2000 -- Apr 2001, July 2001 -- Oct 2002, Sep 2005 -- Aug 2009

\begin{itemize}
    \item Set up individualized learning plans for students in a mixed age classroom (3 to 5-year-olds).
    \item Knowledge of human behavior and performance, individual differences in ability, personality, and
    interests, using different learning styles for student achievement.
    \item Experience implementing and evaluating assessments while tracking progress using verbal and
    written communication and formalized recording methods for semiannual parent/teacher conferences.
    \item Successful in collaborative design, implementation, and supervision of developmentally appropriate
    program including day-to-day operation and curriculum, field trips, and special events.
    \item Achieved team mentor status; training and guiding team members in the classroom.
    \item Schedule and conduct tours of the school for families interested in enrolling.
\end{itemize}

\vspace{1pc}
\textbf{Hillsborough Kids Inc.}\hfill Family Services Counselor \& Care Manager
\smallbreak Tampa, FL\hfill Oct 2002 -- Aug 2005

\begin{itemize}
    \item Crisis intervention, counseling, and protective supervision for children and families.
    \item Researched, developed, and implemented case plans for families in the child welfare system.
    \item Coordinated meetings and therapy for families; supervise parent/child visits.
    \item Attended and participated in court hearings regarding family progress on case plans.
    \item Observed and recorded behaviors of children and families for use in court document writings and hearings.
    \item Facilitated adoptions and foster care services.
    \item Supervise the health and well-being of at-risk children (ages 0-18) in families and residential facilities.
    \item Mentored positive choices and appropriate communication and behavioral interaction among children and families.
    \item Fostered partnerships among children, parents, and the community.
\end{itemize}

\vspace{1pc}
\textbf{Developmental Learning Center}\hfill Assistant Teacher
\smallbreak St. Thomas, U.S. Virgin Islands\hfill Apr 2001 -- Jul 2001


\section*{\mblue Education}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.845in}{0.02cm}}

\vspace{1pc}
\textbf{B.A. Psychology (2000)}\hfill University of Wisconsin--Stout
\bigbreak\textbf{Colorado Early Childhood Teacher Qualification (2010)}\hfill Front Range Community College
\bigbreak\textbf{Yoga Alliance Certified Yoga Teacher (2018)}\hfill Breathe for Change--Denver
\bigbreak\textbf{SMART-1 (Stress Management and Relaxation Techniques in Education) (2018)}\hfill Colorado State University
\bigbreak\textbf{Colorado Initial Teacher License (June 2019)}\hfill Friends Teacher Preparation Program
\bigbreak\textbf{M.A. Learning, Developmental and Family Sciences (expected August 2020)}\hfill University of Colorado--Denver
\smallbreak Concentration in Human Learning and Development

\end{document}


























